### 2021-07-08 rad-icfp-2021/correctness.tex
fixing some refs

In general, categories with products (and more generally monoidal categories) can be equivalently presented in the following three ways. 
Although the three styles of presentation are categorically equivalent, the choice of presentation affects the internal language syntax.
\begin{itemize}
    \item categories, where each arrow has one source and one target. These are most familiar but don’t directly match with a programming syntax (except the categorical abstract machine). 
    \item multicategories, where each arrow has a list of source objects !A$_1,\ldots,$A$_n$! and one target !B!, thought of as a map !A$_1$ $\times\ldots\times$A$_n\to$B!. 
    These are very close to the syntax usually used in typed programming languages \cite{ambek1968deductive,staton2013universal}, 
    thinking of an arrow as a typed term !x$_1$:A$_1,\ldots,$x$_n$:A$_n$ $\vdash$ B!.
    \item concategories, aka coloured props \cite{bonchi2015full,fong2019backprop}, where each arrow has a list of source objects !A$_1\ldots$A$_n$! and a list of target objects !B$_1\ldots$B$_m$!, thought of as a map !A$_1\times\ldots\times$A$_m \to$ B$_1\times\ldots\times$B$_m$!. These match the syntax of the UNF language.
\end{itemize}

>>>>

In general, categories with products (and more generally monoidal categories) can be equivalently presented in the following three ways. 
Although the three styles of presentation are categorically equivalent, the choice of presentation affects the internal language syntax.
\begin{itemize}
    \item categories, where each arrow has one source and one target. These are most familiar but don’t directly match with a programming syntax (except the categorical abstract machine). 
    \item multicategories, where each arrow has a list of source objects !A$_1,\ldots,$A$_n$! and one target !B!, thought of as a map !A$_1$ $\times\ldots\times$A$_n\to$B!. 
    These are very close to the syntax usually used in typed programming languages \cite{lambek1968deductive,staton2013universal}, 
    thinking of an arrow as a typed term !x$_1$:A$_1,\ldots,$x$_n$:A$_n$ $\vdash$ B!.
    \item concategories, aka coloured props \cite{bonchi2015full,fong2019backprop}, where each arrow has a list of source objects !A$_1\ldots$A$_n$! and a list of target objects !B$_1\ldots$B$_m$!, thought of as a map !A$_1\times\ldots\times$A$_m \to$ B$_1\times\ldots\times$B$_m$!. These match the syntax of the UNF language.
\end{itemize}

### 2021-07-08 rad-icfp-2021/relwork.tex
fixing some refs

\noindent \textbf{Correctness of AD in functional languages.}
Several recent work \cite{huot2020correctness,vakar2020reverse,vakar2020denotational,brunel2019backpropagation,barthe2020versatility,mazza2021automatic,ee2020correctness} have focused on correctness of AD in a purely functional setting, 
often leaving efficiency on the side, especially for reverse-mode differentiation. 
We see our work as a complement and a first bridge between these works 
and more practical considerations of efficiency and implementations, 
which often require a lot more care than is acknowledged in more theoretical works.

@@

TODO
\cite{ee2020correctness}: non diff function
\cite{sherman2021}: non diff HO functions
\cite{pearlmutter2008reverse}: based on this
\cite{elliott2018simple}: bit similar because using CT as useful language, but we take impl and opti more seriously.
\cite{shaikhha2019efficient}: similar approach but here more complicated for reverse mode, would be interesting to investigate more loop fusions here.

>>>>

\noindent \textbf{Correctness of AD in functional languages.}
Several recent work \cite{huot2020correctness,vakar2020reverse,vakar2020denotational,brunel2019backpropagation,barthe2020versatility,mazza2021automatic,lee2020correctness} have focused on correctness of AD in a purely functional setting, 
often leaving efficiency on the side, especially for reverse-mode differentiation. 
We see our work as a complement and a first bridge between these works 
and more practical considerations of efficiency and implementations, 
which often require a lot more care than is acknowledged in more theoretical works.

@@

TODO
\cite{lee2020correctness}: non diff function
\cite{sherman2021}: non diff HO functions
\cite{pearlmutter2008reverse}: based on this
\cite{elliott2018simple}: bit similar because using CT as useful language, but we take impl and opti more seriously.
\cite{shaikhha2019efficient}: similar approach but here more complicated for reverse mode, would be interesting to investigate more loop fusions here.
